A Large-Scale Study of the Use of Eval in R

### 2020-08-24 inst/paper/main.tex
Add tags and call site summary

\input{counts.tex}
\input{tag/corpus.tex}

@@

@@

>>>>

\input{tag/counts.tex}
\input{tag/corpus.tex}

@@

Of the \missingNumber packages in our corpus, only \missingNumber packages call
eval. \ref{table:top-ten-package-summary} shows the number of calls to eval made
by the ten most frequent callers to eval. These packages together have
\missingNumber callsites and account for \missingPercentage calls to eval.
Furthermore, the top ten callsites account for \missingPercentage of package
eval calls. A single callsite of \TopTenPackageNameA accounts for over
\missingPercentage calls to eval.

\begin{table}[ht]
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{l|rrr||l|rrr}
      \hline
      \multicolumn{4}{c}{}& \multicolumn{4}{c}{} \\
      \cline{1-4} \cline{5-8}
      Package & Callsites & Calls & Calls \% & Package & Callsites & Calls & Calls \%\\
      \hline
      \TopTenPackageNameA & \TopTenPackageCallsiteCountA & \TopTenPackageCallCountA &\TopTenPackageCallPercA & \TopTenPackageNameF & \TopTenPackageCallsiteCountF & \TopTenPackageCallCountF & \TopTenPackageCallPercF \\
      \TopTenPackageNameB & \TopTenPackageCallsiteCountB & \TopTenPackageCallCountB &\TopTenPackageCallPercB & \TopTenPackageNameG & \TopTenPackageCallsiteCountG & \TopTenPackageCallCountG & \TopTenPackageCallPercG \\
      \TopTenPackageNameC & \TopTenPackageCallsiteCountC & \TopTenPackageCallCountC &\TopTenPackageCallPercC & \TopTenPackageNameH & \TopTenPackageCallsiteCountH & \TopTenPackageCallCountH & \TopTenPackageCallPercH \\
      \TopTenPackageNameD & \TopTenPackageCallsiteCountD & \TopTenPackageCallCountD &\TopTenPackageCallPercD & \TopTenPackageNameI & \TopTenPackageCallsiteCountI & \TopTenPackageCallCountI & \TopTenPackageCallPercI \\
      \TopTenPackageNameE & \TopTenPackageCallsiteCountE & \TopTenPackageCallCountE &\TopTenPackageCallPercE & \TopTenPackageNameJ & \TopTenPackageCallsiteCountJ & \TopTenPackageCallCountJ & \TopTenPackageCallPercJ \\
      \hline
    \end{tabular}
  }
  \label{table:top-ten-package-summary}
  \caption{Distribution of eval calls and callsites in the top ten packages}
\end{table}

@@

\begin{table}[ht]
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{rr|rr|rr}
      \hline
      Callsites & Packages & Callsites & Packages & Callsites & Packages \\
      \hline
      \SiteSummarySiteCountA & \SiteSummaryPackageCountA & \SiteSummarySiteCountF & \SiteSummaryPackageCountF & \SiteSummarySiteCountK & \SiteSummaryPackageCountK \\
      \SiteSummarySiteCountB & \SiteSummaryPackageCountB & \SiteSummarySiteCountG & \SiteSummaryPackageCountG & \SiteSummarySiteCountL & \SiteSummaryPackageCountL \\
      \SiteSummarySiteCountC & \SiteSummaryPackageCountC & \SiteSummarySiteCountH & \SiteSummaryPackageCountH & \SiteSummarySiteCountM & \SiteSummaryPackageCountM \\
      \SiteSummarySiteCountD & \SiteSummaryPackageCountD & \SiteSummarySiteCountI & \SiteSummaryPackageCountI & \SiteSummarySiteCountN & \SiteSummaryPackageCountN \\
      \SiteSummarySiteCountE & \SiteSummaryPackageCountE & \SiteSummarySiteCountJ & \SiteSummaryPackageCountJ & \SiteSummarySiteCountO & \SiteSummaryPackageCountO \\ 
      \hline
    \end{tabular}
  }
  \label{table:site-package-summary}
  \caption{Distribution of callsites across packages}
\end{table}
